\bf Enhancing Scheduling Robustness with Feedback and Biasing

### 2019-04-26 paper.tex
Complete Result and Summary sections.

\title{\bf A Model-Based Scheduling Framework for Enhancing Robustness}

@@

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{figures/BiasVisualization_Simple.pdf}
	\end{center}
	\caption{Illustration of probabilities for a model task requirement
		with bound error as a percentage, $P$, of the actual task
		requirement, $X$, and the effect of the simple bias strategy
		transforming the distribution, given an ideal value for $P$.
		Distribution is assumed to be zero-mean and triangular.}
	\label{fig:cpbias}
\end{figure}

@@

All results were collected using simulations performed using simulator software
developed for previous research \cite{costmin} and \cite{pdpta18} and made
publically available as open source \cite{soasim}.  Workflows and task
requirements are the same as those in \cite{pdpta18} as are simulated error
amounts which ranged from $0.1\%$ up to $90\%$ taken from a uniform
distribution.  For all numeric results for performance the value presented is
an averaged value across ten simulations where the workflows and tasks were
identical but a error term applied to model tasks' requirements were unique.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_NoLoss_NoBias_LowError.pdf}
	\end{center}
	\caption{Histogram of workflows by normalized tardiness comparing
		relative performance of scheduling algorithms with no error (vertical
		bars) and with 0.1\% error applied to the model of the workflow
		requirements (line graphs).  Complete feedback of task completion from
		the actual platform was used, but model platform was, due to
		underestimated task requirements, allowed to model tasks as completing
		and subsequenting scheduling algorithms allowed to schedule additional
		tasks to the machine.}
	\label{fig:noloss-nobias-lowerror}
\end{figure*}

@@

@@

>>>>

\title{\bf Enhancing Scheduling Robustness with Feedback and Biasing}

@@

Four scheduling algorithms were studied in this and previous work.  The first
is First-Come, First-Served (FCFS) which prioritizes scheduling tasks from
workflows which arrived earlier over tasks from workflows that arrived later.
The second is Proportional-Least Laxity First which projects a finish time
of a task's workflow based on the rate of completion of its tasks in the past
and then prioritizes tasks from workflows projected to be completed most tardy
proportional to the overall size of the workflow.  The final two are variants
of the Cost-Minimization Scheduling Algorithm (CMSA) \cite{costmin} which
projects a finish time of a task's workflow (as with PLLF) and uses a cost
function to assign as cost to the projected tardiness.  CMSA is used with two
cost functions: a quadratic cost function and sigmoid cost function.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{figures/BiasVisualization_Simple.pdf}
	\end{center}
	\caption{Illustration of probabilities for a model task requirement
		with bound error as a percentage, $P$, of the actual task
		requirement, $X$, and the effect of the simple bias strategy
		transforming the distribution, given an ideal value for $P$.
		Distribution is assumed to be zero-mean and triangular.}
	\label{fig:sbias}
\end{figure}

@@

All results were collected using simulations performed using simulator software
developed for previous research \cite{costmin} and \cite{pdpta18} and made
publically available as open source \cite{soasim}.  Workflows and task
requirements are the same as those in \cite{pdpta18} as are simulated error
amounts which ranged from $0.1\%$ up to $50\%$ taken from a uniform
distribution.  For all numeric results for performance the value presented is
an averaged value across ten simulations where the workflows and tasks were
identical but a error term applied to model tasks' requirements were unique.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_NoLoss_NoBias_LowAllError.pdf}
	\end{center}
	\caption{Histogram of workflows by normalized tardiness comparing
		relative performance of scheduling algorithms with no error (vertical
		bars) and with 0.1\% error applied to the model of the workflow
		requirements (line graphs).  Complete feedback of task completion from
		the actual platform was used, but model platform was, due to
		underestimated task requirements, allowed to model tasks as completing
		and subsequenting scheduling algorithms allowed to schedule additional
		tasks to the machine.}
	\label{fig:noloss-nobias-lowerror}
\end{figure*}

@@

Figure \ref{fig:nofeedback-cbias-higherror} depicts the effect of the constant
bias strategy in the present of the highest ($50\%$) error tested with no
feedback (the lines of the graph) against the no-error ideal case (the bars
of the graph).  Key results are that for constant bias strategy is of no
help to the FCFS algorithm which completes the majority of workflows with a
normalized tardiness of $10$ or above.  For the PLLF algorithm, nearly as
many workflows are no longer completed on time as for FCFS but the maximum
normalized tardiness of workflows remains bounded at about $4$.  Both
variants of CMSA seem to similarly complete fewer overall workflows on time
through for the Quadratic cost function variant those workflows seem to be
completed mostly at $0.5$ normalized tardiness and below while for the
Sigmoid cost function variant they are spread from normalized tardinesses
under $0.25$ up to $10+$. Although not depicted, for smaller bounded errors,
the constant bias strategy does expectedly better, achieving results nearly
as good as the no-error ideal case for errors up to about $5\%$.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_CompleteHighAllUniformError_WithCBias.pdf}
	\end{center}
	\caption{Histogram of workflows by normalized tardiness comparing
		relative performance of scheduling algorithms in ideal case with no
		error (vertical bars) and with 50\% error applied to the model of the
		workflow requirements (line graphs) given no feedback of task
		completion times and using the constant bias strategy with ideal
		constant to prevent underestimating task requirements in even the
		worst instance of error.}
	\label{fig:nofeedback-cbias-higherror}
\end{figure*}

Neither the proportionate nor simple bias strategies achieve acceptible
results with errors as high as $50\%$.  In Figures
\ref{fig:nofeedback-pbias-mederror} and \ref{fig:nofeedback-sbias-mederror}
the effect of proportionate and simple bias strategies are shown, respectively,
in the case of $5\%$ error with no feedback and ideal bias value $P=5\%$.
In the case of Figure \ref{fig:nofeedback-pbias-mederror} and proportionate
bias strategy all four scheduling algorithms complete about one third fewer
workflows at a normalized tardiness of $-0.25$ and below although most of those
workflows are instead completed at normalized tardiness up to $0$, so they are
still completed before their deadline.  CMSA with both cost functions completes
a few more workflows mildly late (normalized tardiness $0.25$ and below), PLLF
completes more workflows at normalized tardinesses up to $1$, and FCFS a few
more at $4+$.  Overall, the proportionate bias strategy fairly effectively
makes all scheduling algorithms robust to errors up to $5\%$ even without any
actual platform feedback available.

The simple bias strategy achieves an even better result than the proportionate
bias strategy for the $5\%$ bounded error case, showing fewer workflows
shifting from being completed early to completed late.  In fact, the CMSA with
Sigmoid cost function appears to achieve nearly identical results despite no
feedback and up to $5\%$ error when using the simple bias strategy.  It
therefore appears that the small chance for simple bias strategy to still
underestimate task requirements is a better tradeoff than the exagerrated
overestimates produced by the proportionate bias strategy.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_CompleteMediumAllUniformError_WithRBias.pdf}
	\end{center}
	\caption{Histogram of workflows by normalized tardiness comparing
		relative performance of scheduling algorithms in ideal case with no
		error (vertical bars) and with 5\% error applied to the model of the
		workflow requirements (line graphs) given no feedback of task
		completion times and using the proportionate bias strategy with ideal
		$P=5\%$ to prevent underestimating task requirements in even the
		worst instance of error.}
	\label{fig:nofeedback-pbias-mederror}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_CompleteMediumAllUniformError_WithBias.pdf}
	\end{center}
	\caption{Histogram of workflows by normalized tardiness comparing
		relative performance of scheduling algorithms in ideal case with no
		error (vertical bars) and with 5\% error applied to the model of the
		workflow requirements (line graphs) given no feedback of task
		completion times and using the simple bias strategy with ideal
		$P=5\%$ to nearly prevent underestimating task requirements in even the
		worst instance of error.}
	\label{fig:nofeedback-sbias-mederror}
\end{figure*}

@@

In this paper we presented the case for why complete and reliable feedback
of scheduled task completions from an actual platform to the model used for
scheduling decision-making was found to be necessary to achieve robust
performance of scheduling algorithms in previous work \cite{pdpta18}.
Furthermore we have demonstrated the use of partial feedback as insufficient
at achieving that robustness, but have proposed the use of biasing the model
parameters to prevent or reduce the likelihood of the model underestimating
task requirements thereby modeling tasks as completing earlier than their
actual completion.

Three biasing strategies were proposed, each with different assumptions of
what knowledge is available about the error inherent in the model and
different tradeoffs of balancing the amout of overestimation vs. likelihood
of underestimation of task requirements.  Through simulated case studies we
demonstrated that each biasing strategy is useful for achieving robustness
of scheduling algorithm performance at different amount of model error.

Future work that remains includes analysis of whether the combination of
partial feedback with any of the biasing strategies can achieve greater
robustness.  Additionally, other biasing strategies or alternatives to
biasing will be explored to increase robustness or address cases where
the amount of error in the model is unknown.  Finally, the use of more
sophisticated approaches such as machine learning may be applied to either
supplement or replace feedback information from the actual platform.
